Nuclear Wastes bla bla bla

### 2017-01-11 paper.tex
outline done

%\documentclass{article}
\documentclass[preprint,aip,cha]{revtex4-1}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{graphicx}
\graphicspath{ {images/} }
\usepackage{physics}
\usepackage{color}
\newcommand{\red}[1]{\textcolor{red}{\bf #1}}

@@

@@

\section{Radioactivity and nuclear fission}
    Here we detail the nuclear physics underlying most of the things we will talk about
    in this work. We will apply these results in our discussion of nuclear wastes.
    \subsection{Radioactivity}
        \subsubsection{Nuclear shell model}
        By solving Schr\"{o}dinger's equation\cite{k88}

@@

    \subsection{Biological Effects of Radiation}
        The biological effects of radiation have been an important topic for decades. A large
        number of studies took place after the two nuclear bomb explosions in Japan in 1945
        and after disastrous nuclear plant accidents like Chernobyl. Therefore, we have a relatively
        thourough understanding of the consequences of mass exposure to radiation. However, relatively
        little is known about the long-term effects of exposure to small doses, including subtle biological
        changes that lead to cancer and genetic deffects. Here we briefly summarize the known effects.
        \subsubsection{Different kind of radiation?}
        \subsubsection{Quantifying radiation on living tissues}
        The biological impact of radiation depends on the type, power and energy of the radiation, the
        exposure time, and the part of the body exposed. Various quantities have been introduced to
        measure the amount of radiation and the biological impact of radiation. Here we review three
        of these quantities: the absorbed dose, the equivalent dose and the effective dose.

@@

        \subsubsection{Limitations of current studies}
    \subsection{Properties of a neutron}
        Because neutron plays a central role in the physical processes taking
        place in a recator, we should first look at some of its
        properties.
        \subsubsection{Free neutron}
        A free neutron has a half-life of about $10.2$ minutes. \cite{gc01} The Standard
        Model dictates that a free neutron can only go through beta decay, in which a neutron decays
        into a proton, an electron, and an electron antineutrino \red{(source)}. The decay can be denoted by
        \[n^0 \rightarrow p^+ + e^- + \bar{\nu}_e,\]
        where $n$ denotes a neutron, $p^+$ a proton (that is positively charged), $e^-$ a
        (negatively charged) electron and $\bar{\nu}_e$ an electron antineutrino.

@@

        In a radiative capture process, the compound nucleus emits photons, whereas in neutron-induced
        fission, the compound nucleus splits into fragments.
        In fact, not all nuclei can undergo fission.
        Therefore, radiative capture is the only possible neutron absorption process for
        nuclei that are not fissionable.\cite{l66} We will explore neutron-induced fission further in
        section~\ref{sec:fission}. Here we give an example of radiative capture. When a stable form
        of gold ${}^{197}$Au absorbs a neutron, it forms a highly unstable isotope ${}^{198}$Au in its
        excited state and quickly decays into its ground state by emitting $\gamma$ rays. This can be
        written as
        \[{}^{197}\text{Au} + n \rightarrow {}^{198}\text{Au} + \gamma.\]
        Moreover, the isotope ${}^{198}$Au can spontaneously decay into ${}^{198}$Hg via beta decay. This process can
        be seen as the analogy of free neutron beta decay for bound neutrons.

@@

\section{Formation of (High-Level) Nuclear Waste}
    The IAEA classifies nuclear waste by considering the activity content and the half-life
    of the radionuclides (see FIG. \ref{fig:scheme}). Activity content is a measure of how much nuclear activity
    a given amount of wastes contain: a form of waste may possesses a high activity content due to
    a high concentration or high activity.\cite{iaea09}
    \begin{figure}[h]
        \centering
        \includegraphics[width=0.7\textwidth]{wastescheme.png}
        \caption{An illustration of the IAEA classification scheme for nuclear wastes.\cite{iaea09}}
        \label{fig:scheme}
    \end{figure}

@@

    \subsection{Fission products}
    meep
    \subsection{Transuranic radionuclides}
    mop
    \subsection{Trade-offs}
    short huge dose or long small dose?

\section{Disposal}

\section{Future and perspective?}

@@

\pagebreak
\bibliographystyle{aip}
\bibliography{refs}
\appendix
\section{Derivation of Fermi's Golden Rule \#2}
\label{a:fermi}
\section{meep}
\end{document}

>>>>

%\documentclass{article}
\documentclass[preprint,aip,pra]{revtex4-1}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{graphicx}
\graphicspath{ {images/} }
\usepackage{physics}
\usepackage{color}
\newcommand{\red}[1]{\textcolor{red}{\bf #1}}

@@

\title{Nuclear Wastes bla bla bla}

\author{Yuping Huang}%
\affiliation{Department of Physics and Astronomy, Carleton College}

\date{\today}%
\begin{abstract}
    meep
\end{abstract}
\maketitle

\tableofcontents
\newpage

@@

\section{Radioactivity and nuclear fission}
    Here we detail the nuclear physics underlying most of the things we will talk about
    in this work. We will apply these results in our discussion of nuclear wastes.
    \subsection{Radioactivity}
    \subsubsection{Nuclear shell model vs liquid drop model(?)}
        By solving Schr\"{o}dinger's equation\cite{k88}
    \subsubsection{Binding Energy(?)}

@@

    \subsection{Biological Effects of Radiation}
        The biological effects of radiation have been an important topic for decades. A large
        number of studies took place after the two nuclear bomb explosions in Japan in 1945
        and after disastrous nuclear plant accidents like Chernobyl. Therefore, we have a relatively
        thourough understanding of the consequences of mass exposure to radiation. However, relatively
        little is known about the long-term effects of exposure to small doses, including subtle biological
        changes that lead to cancer and genetic deffects. Here we briefly summarize the known effects.
        \subsubsection{Different kinds of radiation and shielding}
        meep
        \subsubsection{Quantifying radiation on living tissues}
        The biological impact of radiation depends on the type, power and energy of the radiation, the
        exposure time, and the part of the body exposed. Various quantities have been introduced to
        measure the amount of radiation and the biological impact of radiation. Here we review three
        of these quantities: the absorbed dose, the equivalent dose and the effective dose.

@@

        \subsubsection{Limitations of current studies}
    \subsection{Properties of a neutron}
        Because neutron plays a central role in the physical processes taking
        place in a recator, we should first look at some of its
        properties.
        \subsubsection{Free neutron}
        A free neutron has a half-life of about $10.2$ minutes. \cite{gc01} The Standard
        Model dictates that a free neutron can only go through beta decay, in which a neutron decays
        into a proton, an electron, and an electron antineutrino \red{(source)}. The decay can be denoted by
        \begin{equation}
            n^0 \rightarrow p^+ + e^- + \bar{\nu}_e,
        \end{equation}
        where $n$ denotes a neutron, $p^+$ a proton (that is positively charged), $e^-$ a
        (negatively charged) electron and $\bar{\nu}_e$ an electron antineutrino.

@@

        In a radiative capture process, the compound nucleus emits photons, whereas in neutron-induced
        fission, the compound nucleus splits into fragments.
        In fact, not all nuclei can undergo fission.
        Therefore, radiative capture is the only possible neutron absorption process for
        nuclei that are not fissionable.\cite{l66} We will explore neutron-induced fission further in
        section~\ref{sec:fission}. Here we give an example of radiative capture. When a stable form
        of gold ${}^{197}$Au absorbs a neutron, it forms a highly unstable isotope ${}^{198}$Au in its
        excited state and quickly decays into its ground state by emitting $\gamma$ rays. This can be
        written as
        \begin{equation}
            {}^{197}\text{Au} + n \rightarrow {}^{198}\text{Au} + \gamma.
        \end{equation}
        Moreover, the isotope ${}^{198}$Au can spontaneously decay into ${}^{198}$Hg via beta decay. This process can
        be seen as the analogy of free neutron beta decay for bound neutrons.

@@

\section{Formation of (High-Level) Nuclear Waste}
    \subsection{Classification of Nuclear Waste}
    The IAEA classifies nuclear waste by considering the activity content and the half-life
    of the radionuclides (see FIG. \ref{fig:scheme}). Activity content is a measure of how much nuclear activity
    a given amount of wastes contain: a form of waste may possesses a high activity content due to
    a high concentration or high activity.\cite{iaea09}
    \begin{figure}[h]
        \centering
        \includegraphics[width=0.7\textwidth]{wastescheme.png}
        \caption{An illustration of the IAEA classification scheme for nuclear wastes.\cite{iaea09}}
        \label{fig:scheme}
    \end{figure}

@@

    \subsection{Comments on lower-level waste and how to deal with them}
    \subsection{Compositions and risks of high-level waste}
    \subsubsection{Fission products(needs shielding)}
        meep
        \subsubsection{Transuranic radionuclides(really bad, needs long-term storage)}
        mop

\section{Re-processing and storage of HLW}
    \subsection{Re-processing of HLW: France and UK}
    \subsection{Requirements for storing HLW}
    \subsection{At-reactor storage}
        \subsubsection{Dry cask storage}
    \subsection{Interim storage}
    \subsection{Necessity of a next-step}

\section{Disposal of HLW}
    \subsection{Comments on partitioning and transmutation}
    \subsection{Survey of possibilities}
    \subsubsection{mention ocean disposal and why it was banned('Ndrangheta)}
    \subsection{Necessity of geological disposal sites}
    \subsection{Requirements of disposal from physics}

\section{Deep Geological Repository}
    \subsection{something general}
    \subsection{Yucca Mountain}
    \subsection{Something related to the French Ciegeo project: licensed reversible disposal site}
    \subsection{Risk calcs: geophysics, mention WIPP}

@@

\pagebreak
\bibliographystyle{aip}
\bibliography{refs}
\appendix
\section{Derivation of Fermi's Golden Rule \#2}
\label{a:fermi}
\end{document}
